---
title: "Multivariate LSTM Stock Forecasting with quantmod and keras3"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
params:
  target: "Open"
  tickers: "TSLA,AMZN,NVDA"
  horizon: 20
  run_pipeline: true
  pivot_order: 2
  pivot_min_prominence: 0
---

This notebook is the R equivalent of `run_yfinance_lstm.py`. It downloads a
rolling five-year daily price history, creates chronological training,
validation, and test sets, trains a multivariate LSTM, evaluates price and
pivot predictions, and provides a recursive future-forecast helper.

The full three-ticker training run is disabled by default because it downloads
live data and trains three deep models. Run it with **Knit with Parameters** and
set `run_pipeline` to `true`, or use:

```r
rmarkdown::render(
  "run_yfinance_lstm.Rmd",
  params = list(run_pipeline = TRUE)
)
```

The `LSTM_TARGET` environment variable, when set, overrides the `target`
parameter. Supported targets are `Open`, `Close`, `High`, and `Low`.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

required_packages <- c("quantmod", "keras3", "jsonlite", "knitr")
missing_packages <- required_packages[
  !vapply(required_packages, requireNamespace, logical(1), quietly = TRUE)
]
if (length(missing_packages) > 0L) {
  stop(
    "Install the required R packages before running this notebook: ",
    paste(missing_packages, collapse = ", ")
  )
}

runtime_cache <- file.path(tempdir(), "lstm-r-cache")
invisible(lapply(
  file.path(runtime_cache, c("matplotlib", "xdg")),
  dir.create,
  recursive = TRUE,
  showWarnings = FALSE
))
Sys.setenv(
  TF_CPP_MIN_LOG_LEVEL = "2",
  MPLCONFIGDIR = file.path(runtime_cache, "matplotlib"),
  XDG_CACHE_HOME = file.path(runtime_cache, "xdg")
)
set.seed(42L)
keras3::set_random_seed(42L)
```

```{r directories_and_features, include=FALSE}
PROJECT_ROOT <- normalizePath(".", mustWork = TRUE)
DATA_DIR <- file.path(PROJECT_ROOT, "data", "yfinance")
MODEL_DIR <- file.path(PROJECT_ROOT, "models", "R_lstm")
REPORT_DIR <- file.path(PROJECT_ROOT, "reports", "R_lstm")
invisible(lapply(c(DATA_DIR, MODEL_DIR, REPORT_DIR), dir.create,
  recursive = TRUE, showWarnings = FALSE
))

FEATURES <- c("Open", "High", "Low", "Close", "Adj Close", "Volume")
TARGETS <- c("Open", "Close", "High", "Low")
LOOKBACK <- 60L
SEED <- 42L
```

## Data and preprocessing helpers

```{r data-helpers}
validate_target <- function(target) {
  if (length(target) != 1L || is.na(target) || !target %in% TARGETS) {
    stop(
      sprintf(
        "target must be one of %s; received %s",
        paste(TARGETS, collapse = ", "),
        deparse(target)
      ),
      call. = FALSE
    )
  }
  target
}

download_data <- function(ticker, end = Sys.Date() + 1L) {
  start <- seq.Date(as.Date(end), by = "-5 years", length.out = 2L)[2L]
  prices <- quantmod::getSymbols(
    ticker,
    src = "yahoo",
    from = start,
    to = as.Date(end),
    auto.assign = FALSE,
    warnings = FALSE
  )

  frame <- data.frame(
    Date = as.Date(zoo::index(prices)),
    Open = as.numeric(quantmod::Op(prices)),
    High = as.numeric(quantmod::Hi(prices)),
    Low = as.numeric(quantmod::Lo(prices)),
    Close = as.numeric(quantmod::Cl(prices)),
    `Adj Close` = as.numeric(quantmod::Ad(prices)),
    Volume = as.numeric(quantmod::Vo(prices)),
    check.names = FALSE
  )
  frame <- frame[stats::complete.cases(frame), c("Date", FEATURES), drop = FALSE]
  frame <- frame[order(frame$Date), , drop = FALSE]
  rownames(frame) <- NULL

  if (nrow(frame) == 0L) {
    stop(sprintf("No data returned for %s", ticker), call. = FALSE)
  }
  frame
}

construct_lstm_data <- function(data, sequence_size, target_idx) {
  data <- as.matrix(data)
  storage.mode(data) <- "double"
  sequence_size <- as.integer(sequence_size)
  target_idx <- as.integer(target_idx)

  if (sequence_size < 1L) {
    stop("sequence_size must be at least 1", call. = FALSE)
  }
  if (target_idx < 1L || target_idx > ncol(data)) {
    stop("target_idx is outside the feature columns", call. = FALSE)
  }

  sample_count <- nrow(data) - sequence_size
  if (sample_count <= 0L) {
    return(list(
      x = array(numeric(), dim = c(0L, sequence_size, ncol(data))),
      y = numeric()
    ))
  }

  x <- array(NA_real_, dim = c(sample_count, sequence_size, ncol(data)))
  y <- numeric(sample_count)
  for (i in seq_len(sample_count)) {
    x[i, , ] <- data[i:(i + sequence_size - 1L), , drop = FALSE]
    y[[i]] <- data[i + sequence_size, target_idx]
  }
  list(x = x, y = y)
}

fit_minmax_scaler <- function(data) {
  data <- as.matrix(data)
  storage.mode(data) <- "double"
  data_min <- apply(data, 2L, min)
  data_max <- apply(data, 2L, max)
  data_range <- data_max - data_min
  data_range[data_range == 0] <- 1

  structure(
    list(
      data_min = data_min,
      data_range = data_range,
      feature_names = colnames(data)
    ),
    class = "lstm_minmax_scaler"
  )
}

transform_minmax <- function(data, scaler) {
  data <- as.matrix(data)
  storage.mode(data) <- "double"
  if (ncol(data) != length(scaler$data_min)) {
    stop("data and scaler must have the same number of features", call. = FALSE)
  }
  sweep(sweep(data, 2L, scaler$data_min, FUN = "-"),
    2L, scaler$data_range, FUN = "/"
  )
}

inverse_target <- function(values, scaler, target_idx) {
  target_idx <- as.integer(target_idx)
  if (target_idx < 1L || target_idx > length(scaler$data_min)) {
    stop("target_idx is outside the scaler features", call. = FALSE)
  }
  as.numeric(values) * scaler$data_range[[target_idx]] + scaler$data_min[[target_idx]]
}

prepare_lstm_data <- function(data, target, lookback = LOOKBACK) {
  target <- validate_target(target)
  lookback <- as.integer(lookback)
  missing_features <- setdiff(FEATURES, names(data))
  if (length(missing_features) > 0L) {
    stop(
      "data is missing feature columns: ",
      paste(missing_features, collapse = ", "),
      call. = FALSE
    )
  }

  n <- nrow(data)
  train_end <- floor(n * 0.70)
  validate_end <- floor(n * 0.85)
  if (train_end <= lookback || validate_end <= train_end || validate_end >= n) {
    stop("data does not contain enough rows for the requested splits and lookback", call. = FALSE)
  }

  train_rows <- seq_len(train_end)
  validate_rows <- seq.int(train_end + 1L, validate_end)
  test_rows <- seq.int(validate_end + 1L, n)
  target_idx <- match(target, FEATURES)

  scaler <- fit_minmax_scaler(data[train_rows, FEATURES, drop = FALSE])
  all_scaled <- transform_minmax(data[, FEATURES, drop = FALSE], scaler)

  train_sequences <- construct_lstm_data(
    all_scaled[train_rows, , drop = FALSE], lookback, target_idx
  )
  validate_context <- seq.int(train_end - lookback + 1L, validate_end)
  validate_sequences <- construct_lstm_data(
    all_scaled[validate_context, , drop = FALSE], lookback, target_idx
  )
  test_context <- seq.int(validate_end - lookback + 1L, n)
  test_sequences <- construct_lstm_data(
    all_scaled[test_context, , drop = FALSE], lookback, target_idx
  )

  list(
    scaler = scaler,
    target_idx = target_idx,
    split_rows = list(
      train = train_rows,
      validate = validate_rows,
      test = test_rows
    ),
    train = c(train_sequences, list(dates = data$Date[(lookback + 1L):train_end])),
    validate = c(validate_sequences, list(dates = data$Date[validate_rows])),
    test = c(test_sequences, list(dates = data$Date[test_rows]))
  )
}
```

## Model construction

The architecture matches the Python implementation: four 100-unit LSTM
layers, a 20% dropout layer after each LSTM, and a one-unit dense output.

```{r model-helper}
build_model <- function(input_shape) {
  model <- keras3::keras_model_sequential(input_shape = as.integer(input_shape)) |>
    keras3::layer_lstm(units = 100L, return_sequences = TRUE) |>
    keras3::layer_dropout(rate = 0.2) |>
    keras3::layer_lstm(units = 100L, return_sequences = TRUE) |>
    keras3::layer_dropout(rate = 0.2) |>
    keras3::layer_lstm(units = 100L, return_sequences = TRUE) |>
    keras3::layer_dropout(rate = 0.2) |>
    keras3::layer_lstm(units = 100L, return_sequences = FALSE) |>
    keras3::layer_dropout(rate = 0.2) |>
    keras3::layer_dense(units = 1L)

  model |> keras3::compile(
    optimizer = "adam",
    loss = "mean_squared_error"
  )
  model
}
```

## Pivot analysis

```{r pivot-helpers}
empty_pivots <- function() {
  data.frame(
    Date = as.Date(character()),
    price = numeric(),
    pivot_type = character(),
    stringsAsFactors = FALSE
  )
}

detect_pivots <- function(dates, prices, pivot_order = 2L,
                          min_prominence = 0) {
  pivot_order <- as.integer(pivot_order)
  if (pivot_order < 1L) {
    stop("pivot_order must be at least 1", call. = FALSE)
  }
  if (length(dates) != length(prices)) {
    stop("dates and prices must have the same length", call. = FALSE)
  }

  dates <- as.Date(dates)
  prices <- as.numeric(prices)
  if (length(prices) < 2L * pivot_order + 1L) {
    return(empty_pivots())
  }

  rows <- list()
  for (i in seq.int(pivot_order + 1L, length(prices) - pivot_order)) {
    neighborhood <- seq.int(i - pivot_order, i + pivot_order)
    other_indices <- neighborhood[neighborhood != i]
    value <- prices[[i]]

    if (value == max(prices[neighborhood]) &&
        value > max(prices[other_indices]) * (1 + min_prominence)) {
      rows[[length(rows) + 1L]] <- data.frame(
        Date = dates[[i]], price = value, pivot_type = "high"
      )
    } else if (value == min(prices[neighborhood]) &&
               value < min(prices[other_indices]) * (1 - min_prominence)) {
      rows[[length(rows) + 1L]] <- data.frame(
        Date = dates[[i]], price = value, pivot_type = "low"
      )
    }
  }

  if (length(rows) == 0L) empty_pivots() else do.call(rbind, rows)
}

empty_pivot_comparison <- function() {
  data.frame(
    pivot_type = character(),
    predicted_date = as.Date(character()),
    true_date = as.Date(character()),
    date_error_days = integer(),
    predicted_price = numeric(),
    true_price = numeric(),
    matched = logical(),
    stringsAsFactors = FALSE
  )
}

compare_pivots <- function(predicted, actual, max_date_gap = 5L) {
  if (nrow(predicted) == 0L && nrow(actual) == 0L) {
    return(empty_pivot_comparison())
  }

  predicted <- predicted[order(as.Date(predicted$Date)), , drop = FALSE]
  actual <- actual[order(as.Date(actual$Date)), , drop = FALSE]
  predicted$Date <- as.Date(predicted$Date)
  actual$Date <- as.Date(actual$Date)
  used_actual <- rep(FALSE, nrow(actual))
  rows <- list()

  if (nrow(predicted) > 0L) {
    for (pred_idx in seq_len(nrow(predicted))) {
      candidate_indices <- which(
        !used_actual & actual$pivot_type == predicted$pivot_type[[pred_idx]]
      )
      match_idx <- NA_integer_
      if (length(candidate_indices) > 0L) {
        gaps <- abs(as.integer(
          actual$Date[candidate_indices] - predicted$Date[[pred_idx]]
        ))
        candidate_order <- order(gaps, actual$Date[candidate_indices])
        nearest <- candidate_indices[candidate_order[[1L]]]
        if (gaps[candidate_order[[1L]]] <= max_date_gap) {
          match_idx <- nearest
        }
      }

      if (is.na(match_idx)) {
        rows[[length(rows) + 1L]] <- data.frame(
          pivot_type = predicted$pivot_type[[pred_idx]],
          predicted_date = predicted$Date[[pred_idx]],
          true_date = as.Date(NA),
          date_error_days = NA_integer_,
          predicted_price = predicted$price[[pred_idx]],
          true_price = NA_real_,
          matched = FALSE
        )
      } else {
        used_actual[[match_idx]] <- TRUE
        rows[[length(rows) + 1L]] <- data.frame(
          pivot_type = predicted$pivot_type[[pred_idx]],
          predicted_date = predicted$Date[[pred_idx]],
          true_date = actual$Date[[match_idx]],
          date_error_days = abs(as.integer(
            predicted$Date[[pred_idx]] - actual$Date[[match_idx]]
          )),
          predicted_price = predicted$price[[pred_idx]],
          true_price = actual$price[[match_idx]],
          matched = TRUE
        )
      }
    }
  }

  unused_actual <- which(!used_actual)
  for (actual_idx in unused_actual) {
    rows[[length(rows) + 1L]] <- data.frame(
      pivot_type = actual$pivot_type[[actual_idx]],
      predicted_date = as.Date(NA),
      true_date = actual$Date[[actual_idx]],
      date_error_days = NA_integer_,
      predicted_price = NA_real_,
      true_price = actual$price[[actual_idx]],
      matched = FALSE
    )
  }

  result <- do.call(rbind, rows)
  result[order(result$predicted_date, result$true_date, na.last = TRUE), , drop = FALSE]
}
```

## Recursive forecast helpers

As in the Python version, future values for non-target features are unknown.
The recursive forecast therefore replaces only the selected target with the
model prediction and carries the latest scaled values of the other features
forward. This is a scenario forecast rather than a complete market simulator.

```{r forecast-helpers}
business_days <- function(last_date, horizon) {
  horizon <- as.integer(horizon)
  if (horizon < 0L) {
    stop("horizon cannot be negative", call. = FALSE)
  }
  if (horizon == 0L) {
    return(as.Date(character()))
  }

  candidate_count <- ceiling(horizon * 7 / 5) + 7L
  candidates <- seq.Date(
    as.Date(last_date) + 1L,
    by = "day",
    length.out = candidate_count
  )
  weekday_number <- as.POSIXlt(candidates)$wday
  candidates[!weekday_number %in% c(0L, 6L)][seq_len(horizon)]
}

forecast_future <- function(model, recent_data, scaler, target, horizon,
                            lookback = LOOKBACK) {
  target <- validate_target(target)
  lookback <- as.integer(lookback)
  horizon <- as.integer(horizon)
  if (nrow(recent_data) < lookback) {
    stop(
      sprintf("recent_data must contain at least %d rows", lookback),
      call. = FALSE
    )
  }
  if (horizon < 1L) {
    stop("horizon must be at least 1", call. = FALSE)
  }

  target_idx <- match(target, FEATURES)
  values <- as.matrix(tail(recent_data[, FEATURES, drop = FALSE], lookback))
  scaled <- transform_minmax(values, scaler)
  forecasts <- numeric(horizon)

  for (step in seq_len(horizon)) {
    model_input <- array(scaled, dim = c(1L, lookback, length(FEATURES)))
    next_scaled <- as.numeric(stats::predict(model, model_input, verbose = 0))[[1L]]
    next_row <- scaled[nrow(scaled), ]
    next_row[[target_idx]] <- next_scaled
    forecasts[[step]] <- inverse_target(next_scaled, scaler, target_idx)
    scaled <- rbind(scaled[-1L, , drop = FALSE], next_row)
  }

  result <- data.frame(
    Date = business_days(tail(recent_data$Date, 1L), horizon),
    forecast = forecasts,
    check.names = FALSE
  )
  names(result)[[2L]] <- target
  result
}

save_forecast_pivots <- function(forecast, ticker, target,
                                 pivot_order = 2L,
                                 min_prominence = 0,
                                 report_dir = REPORT_DIR) {
  target <- validate_target(target)
  pivots <- detect_pivots(
    forecast$Date,
    forecast[[target]],
    pivot_order,
    min_prominence
  )
  dir.create(report_dir, recursive = TRUE, showWarnings = FALSE)
  start <- format(min(as.Date(forecast$Date)), "%Y-%m-%d")
  end <- format(max(as.Date(forecast$Date)), "%Y-%m-%d")
  output <- file.path(
    report_dir,
    sprintf(
      "%s_%s_forecast_pivots_%s_to_%s.csv",
      tolower(ticker), tolower(target), start, end
    )
  )
  utils::write.csv(pivots, output, row.names = FALSE)
  output
}

forecast_ticker <- function(ticker, target, horizon = 20L,
                            pivot_order = 2L,
                            min_prominence = 0) {
  target <- validate_target(target)
  model_path <- file.path(
    MODEL_DIR,
    sprintf("%s_%s_lstm.keras", tolower(ticker), tolower(target))
  )
  scaler_path <- file.path(
    MODEL_DIR,
    sprintf("%s_%s_scaler.rds", tolower(ticker), tolower(target))
  )
  data_path <- file.path(DATA_DIR, sprintf("%s_raw.csv", tolower(ticker)))

  model <- keras3::load_model(model_path)
  scaler <- readRDS(scaler_path)
  recent_data <- utils::read.csv(data_path, check.names = FALSE)
  recent_data$Date <- as.Date(recent_data$Date)
  forecast <- forecast_future(model, recent_data, scaler, target, horizon)
  pivot_output <- save_forecast_pivots(
    forecast, ticker, target, pivot_order, min_prominence
  )
  list(forecast = forecast, pivot_output = pivot_output)
}
```

## Training, evaluation, and reporting

```{r training-helper}
prediction_metrics <- function(actual, predicted) {
  data.frame(
    rmse = sqrt(mean((actual - predicted)^2)),
    mae = mean(abs(actual - predicted))
  )
}

history_epochs <- function(history) {
  as.integer(length(history$metrics$loss))
}

plot_results <- function(data, prepared, predictions, ticker, target,
                         output_path) {
  grDevices::png(output_path, width = 2250, height = 1500, res = 150)
  old_par <- graphics::par(mfrow = c(2L, 1L), mar = c(4, 4, 3, 1))
  on.exit({
    graphics::par(old_par)
    grDevices::dev.off()
  }, add = TRUE)

  graphics::plot(
    data$Date, data[[target]],
    type = "l", col = "black", lwd = 1,
    xlab = "Date", ylab = sprintf("%s price (USD)", target),
    main = sprintf("%s: five-year daily %s price and chronological splits", ticker, target)
  )
  split_rows <- prepared$split_rows
  graphics::abline(v = data$Date[min(split_rows$validate)], col = "orange", lty = 2)
  graphics::abline(v = data$Date[min(split_rows$test)], col = "darkgreen", lty = 2)
  graphics::legend(
    "topleft",
    legend = c(sprintf("Actual %s", target), "Validation start", "Test start"),
    col = c("black", "orange", "darkgreen"),
    lty = c(1, 2, 2),
    bty = "n"
  )
  graphics::grid(col = "grey85")

  all_dates <- do.call(c, lapply(predictions, `[[`, "dates"))
  all_values <- unlist(lapply(
    predictions,
    function(item) c(item$actual, item$predicted)
  ))
  graphics::plot(
    range(all_dates), range(all_values, finite = TRUE),
    type = "n", xlab = "Date", ylab = sprintf("%s price (USD)", target),
    main = sprintf("%s: LSTM next-day %s predictions", ticker, target)
  )
  colors <- c(train = "#1b6ca8", validate = "#d97706", test = "#16803c")
  for (split_name in names(predictions)) {
    item <- predictions[[split_name]]
    graphics::lines(item$dates, item$actual, col = colors[[split_name]], lwd = 1)
    graphics::lines(item$dates, item$predicted,
      col = colors[[split_name]], lwd = 1, lty = 2
    )
  }
  graphics::legend(
    "topleft",
    legend = as.vector(rbind(
      paste(tools::toTitleCase(names(predictions)), "actual"),
      paste(tools::toTitleCase(names(predictions)), "predicted")
    )),
    col = rep(colors, each = 2L),
    lty = rep(c(1, 2), times = length(colors)),
    ncol = 3L,
    bty = "n"
  )
  graphics::grid(col = "grey85")
  invisible(output_path)
}

run_ticker <- function(ticker, target) {
  target <- validate_target(target)
  set.seed(SEED)
  keras3::set_random_seed(SEED)

  data <- download_data(ticker)
  data_path <- file.path(DATA_DIR, sprintf("%s_raw.csv", tolower(ticker)))
  utils::write.csv(data, data_path, row.names = FALSE)

  prepared <- prepare_lstm_data(data, target, LOOKBACK)
  scaler_path <- file.path(
    MODEL_DIR,
    sprintf("%s_%s_scaler.rds", tolower(ticker), tolower(target))
  )
  saveRDS(prepared$scaler, scaler_path)

  model <- build_model(c(LOOKBACK, length(FEATURES)))
  model_path <- file.path(
    MODEL_DIR,
    sprintf("%s_%s_lstm.keras", tolower(ticker), tolower(target))
  )
  callbacks <- list(
    keras3::callback_model_checkpoint(
      filepath = model_path,
      monitor = "val_loss",
      save_best_only = TRUE,
      mode = "min"
    ),
    keras3::callback_early_stopping(
      monitor = "val_loss",
      patience = 25L,
      restore_best_weights = TRUE
    )
  )
  history <- model |> keras3::fit(
    x = prepared$train$x,
    y = prepared$train$y,
    validation_data = list(prepared$validate$x, prepared$validate$y),
    epochs = 50L,
    batch_size = 64L,
    callbacks = callbacks,
    verbose = 0L
  )

  best_model <- keras3::load_model(model_path)
  predictions <- lapply(
    c("train", "validate", "test"),
    function(split_name) {
      split <- prepared[[split_name]]
      list(
        actual = inverse_target(
          split$y, prepared$scaler, prepared$target_idx
        ),
        predicted = inverse_target(
          as.numeric(stats::predict(best_model, split$x, verbose = 0L)),
          prepared$scaler,
          prepared$target_idx
        ),
        dates = split$dates
      )
    }
  )
  names(predictions) <- c("train", "validate", "test")

  metrics <- data.frame(
    ticker = ticker,
    target = target,
    rows = nrow(data),
    start = format(min(data$Date), "%Y-%m-%d"),
    end = format(max(data$Date), "%Y-%m-%d"),
    train_rows = length(prepared$split_rows$train),
    validate_rows = length(prepared$split_rows$validate),
    test_rows = length(prepared$split_rows$test),
    epochs_run = history_epochs(history),
    stringsAsFactors = FALSE
  )
  for (split_name in names(predictions)) {
    split_metrics <- prediction_metrics(
      predictions[[split_name]]$actual,
      predictions[[split_name]]$predicted
    )
    metrics[[paste0(split_name, "_rmse")]] <- split_metrics$rmse
    metrics[[paste0(split_name, "_mae")]] <- split_metrics$mae
  }

  pivot_rows <- lapply(names(predictions), function(split_name) {
    item <- predictions[[split_name]]
    predicted_pivots <- detect_pivots(
      item$dates, item$predicted,
      params$pivot_order, params$pivot_min_prominence
    )
    actual_pivots <- detect_pivots(
      item$dates, item$actual,
      params$pivot_order, params$pivot_min_prominence
    )
    comparison <- compare_pivots(predicted_pivots, actual_pivots)
    data.frame(split = rep(split_name, nrow(comparison)), comparison)
  })
  pivot_dates <- do.call(rbind, pivot_rows)
  pivot_path <- file.path(
    REPORT_DIR,
    sprintf(
      "%s_%s_pivots_%s_to_%s.csv",
      tolower(ticker), tolower(target),
      format(min(data$Date), "%Y-%m-%d"),
      format(max(data$Date), "%Y-%m-%d")
    )
  )
  utils::write.csv(pivot_dates, pivot_path, row.names = FALSE)

  plot_results(
    data, prepared, predictions, ticker, target,
    file.path(REPORT_DIR, sprintf("%s_%s_results.png", tolower(ticker), tolower(target)))
  )
  metrics
}
```

## Execute the pipeline

```{r run-pipeline}
TARGET <- validate_target(Sys.getenv("LSTM_TARGET", unset = params$target))
TICKERS <- trimws(strsplit(params$tickers, ",", fixed = TRUE)[[1L]])
results <- NULL

if (isTRUE(params$run_pipeline)) {
  results <- do.call(rbind, lapply(TICKERS, run_ticker, target = TARGET))
  utils::write.csv(
    results,
    file.path(REPORT_DIR, "metrics.csv"),
    row.names = FALSE
  )
  jsonlite::write_json(
    results,
    file.path(REPORT_DIR, "metrics.json"),
    dataframe = "rows",
    pretty = TRUE,
    auto_unbox = TRUE,
    na = "null"
  )
  knitr::kable(results, digits = 4)
} else {
  cat("Pipeline execution is disabled. Set `run_pipeline: true` to train the models.")
}
```

After a model has been trained, generate a 20-business-day recursive forecast
and save its predicted pivots with:

```{r forecast-example, eval=FALSE}
tsla_forecast <- forecast_ticker(
  "TSLA",
  target = TARGET,
  horizon = params$horizon,
  pivot_order = params$pivot_order,
  min_prominence = params$pivot_min_prominence
)
tsla_forecast$forecast
tsla_forecast$pivot_output
```
